An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-01 Paper.tex
Fix typo in formula for asymptotic variance
Changes the formula for g_t so that the summation uses s, not t, as an index.
Add submodules for external libraries
Adds submodules for external libraries used in the paper and changes the source
code to use these local copies instead of installed versions.
Clean up build process
Shortens file names and simplifies build path for the paper and monte carlo.  Also sets a
few parameters to govern empirics and monte carlo (this was done through the noweb
document before).

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting for helpful comments.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}
